Variation in site entropy explains differences in structure-sequence relationships of proteins

### 2015-06-10 manuscript/manuscript.tex
Making final first edits

\begin{abstract}
Recent work has shown that structural properties are capable of predicting site-specific sequence variability for a given protein. However, the strength and significance of these structure-sequence relations appear to vary widely among different proteins, with absolute correlation strengths ranging from $0.1$ to $0.8$. There have two works that have investigated structural predictors of site variability which both present different results based on the strength of correlations of structural predictors. According to \cite{Yehetal2014a}, both solvent accessibility and local packing density are predictors of site-wise variability with local packing density being strongest predictor of site-wise variability. However, recently, \cite{Shahmoradietal2014} compared local packing density, residue flexibility, and solvent accessibility in viral proteins and found that relative solvent accessibility is a stronger predictor of site-wise variability. In addition, the strength of correlations with structural predictors were weaker in \cite{Shahmoradietal2014}.  Here we present research that suggests that differences in the correlations between these two datasets are due to differences in the site variability among proteins within in each dataset. Specifically proteins with a larger variance in entropy among sites exhibit stronger structure-sequence correlations between both local packing density and solvent accessibility. 
\end{abstract}
\vfill
\vfill
\def\thefootnote{\fnsymbol{footnote}}
\setcounter{footnote}{0}

@@

The effect of protein-protein interactions(Fraser 2002)

Proteins are subject to a number of biophysical and functional constraints \citep{Scherreretal2012, Wilkeetal2010, Sikoseketal2014, Liberlesetal2009, Huangetal2014, Fraseretal2002, Liaoetal2010, Serohijosetal2012}. These constraints result in site-specific patterns of sequence variability within a protein. Recently several site-specific structural properties that can explain patterns of sequence variability in proteins have been identified. One of the earliest examples was Relative Site Accessibility (RSA). \cite{Fransozaetal2009} identified RSA as the strongest predictor of evolutionary rate and found that residues that are buried within the core of proteins tend to be more conserved than exposed residues close to the surface of the protein. In their analysis, they considered the ability of both RSA and various definitions of residue packing density to predict evolutionary rate. They found that RSA and evolutionary rate shared a significant linear relationship. Afterwards, several other works  also found that RSA as a significant predictor of evolutionary rate and supported this linear relationship \citep{Ramseyetal2011, Scherreretal2012}. However, these papers all have the same flaw. During the course of their analysis they binned the protein sites and averaged over all sites within a bin when determining the trend of RSA. This process may have produced artifacts that account for this strong linear trend between RSA and evolutionary rate. \\
\indent Recently, \cite{Yehetal2014a} performed a similar analysis on a series of enzyme monomer proteins and found that packing density, as defined by Contact Number and Weighted Contact Number \citep{Liaoetal2005, Yehetal2014a, Huangetal2014}, was the strongest determinant of site variability.  Soon Afterwards, \cite{Shahmoradietal2014} also performed a site-wise analysis on a series of viral proteins. In this analysis they found that RSA had a slightly stronger correlation with site variability as opposed to local packing density.  Moreover, the effect seen between CN and WCN was of a much smaller magnitude as compared to \cite{Yehetal2014a}. It is not well understood the reasoning behind the difference in magnitude in the correlations seen between the two studies. Here we attempt to reconcile the work done in this area. We find that site variability is the primary determinant of the strength of structure-sequence relationships and some differences in previous work can be explained in terms of differing levels of site variability. \\

@@

Although it is clear that structure plays a role in the evolution of proteins, it is not clear to what extent protein structure constrains sequence variability. To date there have been conflicting reports about the strength of structure-sequence correlations \citep{Yehetal2014b, Shahmoradietal2014}. Therefore we sought to determine the main determinants of structure-sequence correlations within proteins. First, we calculated the strength between the structural properties and site variability by calculating the Spearman correlation, $\rho$,  between the structural property (solvent exposure and local packing density) and site variability, as measured by either evolutionary rate or site entropy. On average the correlations between CN and entropy are larger in absolute magnitude in the enzyme proteins as compared to viral proteins. The average $\rho$ between each structural property and each measure of site variability (entropy and evolutionary rates) can be seen in Table \ref{table:entropy_stats}  and Table \ref{table:rate_stats}. The viral proteins experience much lower site variability. Figure 1 shows the correlations between CN and entropy for the viral and enzyme proteins. Even though on average the correlations in the enzyme proteins are larger as reported by \cite{Yehetal2014a}, the viral proteins still have correlation strengths that are comparable to some of the enzyme proteins with lower correlations.

\indent For a given protein its mean entropy and the variance might be different. A protein can have a high mean entropy but have a low variance and vice versa. Figure \ref{fig:protein_ex_plot}A details the relationship between the average entropy across sites within proteins and the variance of entropy across sites. Additionally, the distribution of variance varies greatly between proteins even when they from the same dataset (Figure \ref{fig:protein_ex_plot}B). Therefore the mean entropy of a protein as well as the variance in entropy at sites may be predictive for structure-sequence relationships.

\indent  The average site entropy of a given protein does not seem to be a significant determinant of the strength of structural correlations (Figures \ref{fig:entropy_cn_cor}A, \ref{fig:entropy_wcn_cor}A, \ref{fig:entropy_rsa_cor}A). However, when examining the variance of entropy there is a clear trend within the enzyme proteins.  Proteins with a higher variance in site variability across the protein typically higher  correlations in magnitude (Figures \ref{fig:entropy_cn_cor}B, \ref{fig:entropy_wcn_cor}B, \ref{fig:entropy_rsa_cor}B). If you extrapolate the trend from the enzyme proteins, the viral proteins follow a similar trend. The correlation between the $\rho$ between RSA and entropy and the variance of entropy is positive. Proteins with a larger variance in site entropy have the strongest correlations. The correlation between local packing density (both WCN and CN) and the variance of entropy is negative. Unlike entropy, there is no relationship between the variance of evolutionary rates at sites and any of the measured structural properties (Figures \ref{fig:var_rate_cor}, \ref{fig:var_rate_rsa_cor}). There also is a wide spread in the variance of the evolutionary rates across proteins for both the enzyme and viral proteins.

\indent Although both evolutionary rate, as measured by Rate4Site and entropy are measures of site variability, these quantities are distinctly different. Rate4Site measures the rate at which a site changes over time whereas site entropy measure the absolute variation at a site. A site may have a high evolutionary rate if it changes  frequently between the same few amino acids but have low entropy. It appears that the rate at which a site evolves is not important for predicting the strength of structure-sequence relationships. However, the absolute amount of variation at a site can be used to predict the strength of structure-sequence relationships.

@@

\indent However, when looking at the variance in entropy there are some stark differences. For all structural predictors (i.e., CN, WCN and RSA), the variance in entropy at sites within a protein is a significant predictor of the strength of structure-sequence relations. For packing density, proteins with a larger variance in site-wise entropy have more negative correlations that are higher in magnitude. Proteins with a higher variance in entropy tend to have stronger RSA-Entropy correlations. When using variance and dataset as predictors of structure-sequence correlations, dataset was not a significant predictor in any model. When looking at the variance of entropy, proteins within both datasets at in a similar fashion and overall trends seen between the variance of site variation and the strength of structure-sequence relationships is preserved across both datasets.

@@

There has been previous work that has illuminated several factors that determine the rate at which proteins evolve \citep{Fraseretal2002, Drummondetal2008, Wilkeetal2010, Yangetal2012}. Some of these factors include: expression level \citep{Drummondetal2008, Wilkeetal2010, Paletal2001, Subramanianetal2004}, interactions with other protein partners \citep{Fraseretal2002, Yangetal2012, Minterisetal2005, Pangetal2010}  and selection for the costs of misfolding \citep{Drummondetal2005}.

\indent Proteins are under a number of constraints for function \citep{Liberlesetal2009}. Biophysical considerations that have been shown to affect function include: selection for protein stability and proper folding \citep{Drummondetal2005}, specificity for protein binding \citep{Zarrinparetal2003}  and selection against non-specific and extraneous binding \citep{Levyetal2012}, selection to minimize protein aggregation \citep{DePristoetal2005}  and protein structure \citep{Fransozaetal2009, Fransozaetal2012, Yehetal2014a, Yehetal2014b, Shahmoradietal2014, Echaveetal2015, Huangetal2014}. Recently there have been several works that have looked into the effect of protein structure on protein function. Local packing density and solvent accessibility have been emerged as two structural predictors that have been showed to predict site variability \citep{Yehetal2014a, Yehetal2014b, Shahmoradietal2014, Fransozaetal2009, Bustamanteetal2000}.

\indent Structure imposes constraints on the evolution of proteins. Therefore structural predictors can be used to predict the variability at sites. Two main determinants of variability at protein sites are solvent accessibility and local packing density. Sites that are on surface of the protein tend to have higher solvent accessibility and exhibit more site variability. Sites that are densely packed and have more contacts tend to evolve slower and exhibit less sequence variability. However, the strength of how well these two structural quantities (local packing density and solvent accessibility) has not been clearly explained. \cite{Yehetal2014a} examined the effect of using solvent accessibility and local packing density as measures of predicting site-wise variability. They found that both were predictors. However, \cite{Shahmoradietal2014} performed the same analysis on viral proteins and found that will both were predictors of stir-wise variability, the correlations between these two structural predictors and site variability were significantly lower.

\indent Here we examined the relationship between site variability and the strength of structure-sequence relationships in order to dissect the nature of the correlation between structural properties and site variability. We found that proteins with a larger variance in site variability as measured by sequence entropy, have stronger structure-sequence relationships on average. However, when looking at the mean entropy values of proteins there is a distinct difference between the virus and enzyme datasets. Overall the enzyme proteins have more site variability than the viral proteins. When predicting structure-sequence relationships the variance in site variability among proteins is a better predictor than mean site variability.  \indent Additionally the reason that the enzyme proteins in \cite{Yehetal2014a} had higher correlation coefficients is that on average, the enzyme proteins have larger variance in entropy as compared to the virus proteins of \cite{Shahmoradietal2014}. Moreover, since the variance in entropy is a more significant predictor of correlations in local packing density, an increased level of variance in site variability will have a larger effect on the local packing density correlations. It appears that site entropy and evolutionary rate are not equal measures of site variability in terms of predicting the strength of structure-sequence relationships. Finally, the variance in evolutionary rate among sites of a protein has a smaller an effect on the correlation magnitude as compared to entropy. This suggests that the absolute variability at sites is a better predictor of whether structural determinants can be used to predict variability at sites  as opposed to evolutionary rate. Therefore when examining structural determinants of site variability, entropy is a may be a more meaningful quantity.

@@

    \begin{figure}[H]
            \centerline{\includegraphics[width=7.5in]{entropy_cn_cor.pdf}}     
            \caption{Correlations between Contact Number (CN) and Entropy. For each protein we calculate the Spearman Correlation coefficient between CN and entropy at each site within the protein. A) Comparison between the correlation coefficients and mean entropy of site in each protein. The line indicates a linear regression through the enzyme proteins with mean entropy as a single predictor of the spearman correlations. B) Comparison between correlation coefficients and the variance of entropy of each protein. The enzyme proteins are colored in black and the virus proteins are visualized in red. For both WCN and CN the viral proteins have lower mean entropy and variance of entropy. The line indicates a linear regression through the enzyme proteins with variance entropy as a single predictor of the spearman correlations. Proteins with a larger variance in site entropy among sites tend to smaller CN-Entropy correlations in magnitude. Note: The entropy values in \cite{Shahmoradietal2014} were scaled.}
            \label{fig:entropy_cn_cor}
    \end{figure}

@@

Make a table of the mean correlations and variance from both papers.

>>>>

\begin{abstract}
Recent work has shown that structural properties are capable of predicting site-specific sequence variability for a given protein. However, the strength and significance of these structure-sequence relations appear to vary widely among different proteins, with absolute correlation strengths ranging from $0.1$ to $0.8$. Recently two works that have investigated structural predictors of site variability which both present different results based on the strength of correlations of structural predictors. According to \cite{Yehetal2014a}, both solvent accessibility and local packing density are predictors of site-wise variability with local packing density being strongest predictor of site-wise variability. However, recently, \cite{Shahmoradietal2014} compared local packing density, residue flexibility, and solvent accessibility in viral proteins and found that relative solvent accessibility is a stronger predictor of site-wise variability. In addition, the strength of correlations with structural predictors were weaker in \cite{Shahmoradietal2014}.  Here we present research that suggests that differences in the correlations between these two datasets are due to differences in the site variability among proteins within in each dataset. Specifically proteins with a larger variance in entropy among sites exhibit stronger structure-sequence correlations between both local packing density and solvent accessibility. 
\end{abstract}
\vfill
\vfill
\def\thefootnote{\fnsymbol{footnote}}
\setcounter{footnote}{0}

@@

Proteins are subject to a number of biophysical and functional constraints \citep{Scherreretal2012, Wilkeetal2010, Sikoseketal2014, Liberlesetal2009, Huangetal2014, Fraseretal2002, Liaoetal2010, Serohijosetal2012}. These constraints result in both global patterns between proteins and site-specific patterns of sequence variability within proteins. Recently several site-specific structural properties that can explain patterns of sequence variability in proteins have been identified. One of the earliest examples was Relative Site Accessibility (RSA). \cite{Fransozaetal2009} identified RSA as the strongest predictor of evolutionary rate and found that residues that are buried within the core of proteins tend to be more conserved than exposed residues close to the surface of the protein. In their analysis, they considered the ability of both RSA and various definitions of residue packing density to predict evolutionary rate. They found that RSA and evolutionary rate shared a significant linear relationship. Afterwards, several other works  also found that RSA as a significant predictor of evolutionary rate and supported this linear relationship \citep{Ramseyetal2011, Scherreretal2012}. However, these papers all have the same flaw. During the course of their analysis they binned the protein sites and averaged over all sites within a bin when determining the trend of RSA. This process may have produced artifacts that account for this strong linear trend between RSA and evolutionary rate. \\
\indent Recently, \cite{Yehetal2014a} performed a similar analysis on a series of enzyme monomer proteins and found that packing density, as defined by Contact Number and Weighted Contact Number \citep{Liaoetal2005, Yehetal2014a, Huangetal2014}, was the strongest determinant of site variability.  Soon Afterwards, \cite{Shahmoradietal2014} also performed a site-wise analysis on a series of viral proteins. In this analysis they found that RSA had a slightly stronger correlation with site variability as opposed to local packing density.  Moreover, the effect seen between CN and WCN was of a much smaller magnitude as compared to \cite{Yehetal2014a}. It is not well understood the reasoning behind the difference in magnitude in the correlations seen between the two studies. Here we attempt to reconcile the work done in this area. We find that site variability is the primary determinant of the strength of structure-sequence relationships and some differences in previous work can be explained in terms of differing levels of site variability. \\

@@

Although it is clear that structure plays a role in the evolution of proteins, it is not clear to what extent protein structure constrains sequence variability. To date there have been conflicting reports about the strength of structure-sequence correlations \citep{Yehetal2014b, Shahmoradietal2014}. Therefore we sought to determine the main determinants of the strength of structure-sequence correlations within proteins. First, we calculated the strength between the structural properties and site variability by calculating the Spearman correlation, $\rho$, between the structural property (solvent exposure and local packing density) and site variability, as measured by either evolutionary rate or site entropy. The magnitude of these correlations allows us to determine the strength of solvent accessibility-site variability and local packing density - site variability correlations. For our analysis we used two measures of site variability, Shannon entropy and evolutionary rate. We calculated the LPD-site variability correlations for two types of local packing density: contact number (CN) and weighted contact number. We calculated the correlations for two sets of proteins. One was a set of monomeric enzyme proteins and the other was a set of virus proteins.

\indent On average the correlations between CN and entropy are larger in absolute magnitude in the enzyme proteins as compared to viral proteins. The average $\rho$ between each structural property and each measure of site variability (entropy and evolutionary rates) can be seen in Tables \ref{table:entropy_stats} and \ref{table:rate_stats}. Both CN and WCN are positively correlated with  both measures of site variability. Residues that are more tightly packed (i.e., have more contacting neighbors) are more constrained and less variable. Solvent accessibility, as measured by relative solvent accessibility (RSA) is negatively correlated with site variability. Residues that are exposed on the surface of the protein are less constrained and exhibit more site variability. Both of these trends have been noted previously \citep{Yehetal2014a, Yehetal2014b, Shahmoradietal2014, Liaoetal2005, Fransozaetal2009}. Although similar in sign, the correlations between all structure-sequence relationships are smaller in magnitude for the virus proteins (Table \ref{table:rate_stats}). However, even though on average the correlations in the enzyme proteins are larger as reported by \cite{Yehetal2014a}, the viral proteins still have correlation strengths that are comparable to some of the enzyme proteins with lower correlations (Figures \ref{fig:entropy_cn_cor}, \ref{fig:entropy_wcn_cor}, \ref{fig:entropy_rsa_cor}).

\indent As noted earlier, the virus proteins have lower levels of site variability (Figures \ref{fig:entropy_cn_cor}, \ref{fig:entropy_wcn_cor}, \ref{fig:entropy_rsa_cor}). Due to this fact, we investigated the effect of site variability on the structure-sequence correlations since the viral proteins have lower correlations overall as well. When examining the effect of site variability on the strength of structure-sequence correlations, we looked at both the variance of site variability and the mean of site variability. For a given protein its mean entropy and the variance might be different and both of these quantities measure different sequence variably properties. A protein can have a high mean entropy but have a low variance and vice versa. Figure \ref{fig:protein_ex_plot}A details the relationship between the average entropy across sites within proteins and the variance of entropy across sites. Additionally, the distribution of variance varies greatly between proteins even when they are from the same dataset (Figure \ref{fig:protein_ex_plot}B). Therefore the mean entropy of a protein as well as the variance in entropy at sites may be predictive for structure-sequence relationships.

\indent The average site entropy of a given protein does not seem to be a significant determinant of the strength of structural correlations (Figures \ref{fig:entropy_cn_cor}A, \ref{fig:entropy_wcn_cor}A, \ref{fig:entropy_rsa_cor}A). However, when examining the variance of entropy there is a clear trend within the enzyme proteins.  Proteins with a higher variance in site variability across the protein typically have higher  correlations in magnitude (Figures \ref{fig:entropy_cn_cor}B, \ref{fig:entropy_wcn_cor}B, \ref{fig:entropy_rsa_cor}B).The correlation between the $\rho$ between RSA and entropy and the variance of entropy is positive. Proteins with a larger variance in site entropy have the strongest correlations. The correlation between the $\rho$ between local packing density (both WCN and CN) and entropy and the variance of entropy is negative. Proteins with more variance in entropy have lower correlations in magnitude. Unlike entropy, there is no relationship between the variance of evolutionary rates at sites and any of the measured structural properties (Figures \ref{fig:var_rate_cor}, \ref{fig:var_rate_rsa_cor}). There also is a wide spread in the variance of the evolutionary rates across proteins for both the enzyme and viral proteins.  If you extrapolate the trend from the enzyme proteins, the viral proteins follow a similar trend.

\indent Although both evolutionary rate, as measured by Rate4Site, and entropy are measures of site variability, these quantities are distinctly different. Rate4Site measures the rate at which a site changes over time whereas site entropy measure the absolute variation at a site. A site may have a high evolutionary rate if it changes frequently between the same few amino acids but have low entropy. It appears that the rate at which a site evolves is not important for predicting the strength of structure-sequence relationships. There is no relationship between the variance of evolutionary rate and any of the structure-sequence relationships (Figures \ref{fig:var_rate_cor}, \ref{fig:var_rate_rsa_cor}). However, the absolute amount of variation at a site, as measured by mean entropy, can be used to predict the strength of structure-sequence relationships.

@@

\indent However, when looking at the variance in entropy there are some stark differences. For all structural predictors (i.e., CN, WCN and RSA), the variance in entropy at sites within a protein is a significant predictor of the strength of structure-sequence relations. For packing density, proteins with a larger variance in site-wise entropy have more negative correlations that are higher in magnitude. Proteins with a higher variance in entropy tend to have stronger RSA-Entropy correlations. When using variance and dataset as predictors of structure-sequence correlations, dataset was not a significant predictor in any model. When looking at the variance of entropy, proteins within both datasets at in a similar fashion and overall trends seen between the variance of site variation and the strength of structure-sequence relationships is preserved across both datasets. In summary, site variability appears to be the main determinant of protein structure-sequence relationships with the variance in entropy at a site as the best predictor of magnitude.

@@

There has been previous work that has illuminated several factors that determine the rate at which proteins evolve. Some of these factors include: expression level \citep{Drummondetal2008, Wilkeetal2010, Paletal2001, Subramanianetal2004}, interactions with other protein partners \citep{Fraseretal2002, Yangetal2012, Minterisetal2005, Pangetal2010} and selection for the costs of misfolding \citep{Drummondetal2005}. Recently the effect of biophysical constraints on sequence variability have been considered. Biophysical considerations that have been shown to affect function include: selection for protein stability and proper folding \citep{Drummondetal2005}, selection for protein binding specifity \citep{Zarrinparetal2003}  and selection against non-specific and extraneous binding \citep{Levyetal2012}, selection to minimize protein aggregation \citep{DePristoetal2005} and protein structure \citep{Fransozaetal2009, Fransozaetal2012, Yehetal2014a, Yehetal2014b, Shahmoradietal2014, Echaveetal2015, Huangetal2014}.

\indent There have been several works that have looked into the effect of protein structure on protein function. Local packing density and solvent accessibility have been emerged as two structural predictors that have been showed to predict site variability \citep{Yehetal2014a, Yehetal2014b, Shahmoradietal2014, Fransozaetal2009, Bustamanteetal2000}. Sites that are on surface of the protein tend to have higher solvent accessibility and exhibit more site variability. Sites that are densely packed and have more contacts tend to evolve slower and exhibit less sequence variability. However, the strength of how well these two structural quantities (local packing density and solvent accessibility) correlate with variability at sites has not been clearly explained. \cite{Yehetal2014a} examined the effect of using solvent accessibility and local packing density as measures of predicting site-wise variability. They found that both were significant predictors. However, \cite{Shahmoradietal2014} performed the same analysis on viral proteins and found that while both were predictors of stie-wise variability, the correlations between these two structural predictors and site variability were significantly lower.

\indent Here we examined the relationship between site variability and the strength of structure-sequence relationships in order to dissect the nature of the correlation between structural properties and site variability. We used both enzyme proteins and virus proteins in our analysis. When looking at the mean entropy values of proteins there is a distinct difference between the virus and enzyme datasets. Overall the enzyme proteins have more site variability than the viral proteins.  We found that proteins with a larger variance in site variability as measured by sequence entropy, have stronger structure-sequence relationships on average and that when predicting structure-sequence relationships the variance in site variability among proteins is a better predictor than mean site variability.  Both \cite{Yehetal2014a} and \cite{Shahmoradietal2014} report different levels of magnitude between LPD and RSA and site variability. According to our analysis, one reason that the enzyme proteins in \cite{Yehetal2014a} had higher correlation coefficients is that, on average, the enzyme proteins have a larger variance in entropy as compared to the virus proteins of \cite{Shahmoradietal2014}.

\indent For all proteins, It appears that site entropy and evolutionary rate are not equal measures of site variability in terms of predicting the strength of structure-sequence relationships. The variance in evolutionary rate among sites of a protein has a smaller an effect on the correlation magnitude as compared to entropy. This suggests that the absolute variability at sites is a better predictor of whether structural determinants can be used to predict variability at sites  as opposed to evolutionary rate. Therefore when examining structural determinants of site variability, entropy may be a more meaningful quantity. The variance in entropy of a protein measures the variation in site variability among sites within a protein. The variance in entropy is not necessarily related to high sequence divergence. If divergence is high for a given protein but all sites are have equal levels of divergence, then the variance in entropy for a protein will be low. The same can be said for proteins with sites that are equal in terms of having a low level of variability among sites. If a protein has sites that are extremely variable (ex. some sites that are highly conserved and some that are less conserved), then they will have an have a high variance in entropy.  A larger variation in variability within a protein allows a larger range of correlations with structural quantities. If all sites have similar levels of divergence (ex. low divergence or high divergence) then the dynamic range of correlations you expect to see with structural properties is limited.

\indent We performed our analysis on two type of protein datasets, viral protein and enzyme proteins in order to verify the generality of our analysis. Both proteins exhibit some of the same selective pressures such as selection for stability and pressure to fold and adopt the correct native conformation. However, these proteins are very different in terms of function. Enzymes are used to catalyze chemical actions and as such have additional constraints such as structural constraints for a proper active site for catalytic function.  On the other hand, viruses use their protein to infect and replicate within their hosts. These proteins are utilized to perform a variety of necessary functions for viral replication such as host cellular entry \citep{Radoshitskyetal2007, Allisonetal2014} and nuclear importation \citep{Schalleretal2014}. As host immune systems attack these viruses, these viruses evolve to escape from these host mechanisms resulting in signatures of positive selection within these proteins. There are several examples of positive selection seen in viral proteins (for a review see: \cite{Sironietal2015}).

\indent Because of the difference for selective pressures for function facing these protein types there could different constraints on sequence variability. Indeed, we find that on average the enzyme proteins have more site variability and that virus proteins have a smaller spread in site variability. Most of the viral proteins analyzed have very low variably while the enzyme dataset has proteins with low-range, mid-range and high-range proteins in terms of site variability. Additionally the enzyme proteins are also more variability in terms of site variability of site within a protein as evidence by the variance in entropy. These results there are structural additional constraints that are different within viral proteins and enzyme proteins. Indeed recently \cite{Meyeretal2015} found that a geometrical model that includes distance to the receptor-binding region in Influenza A H3 hemmagglutinin (HA) was able to explain some of the the variance seen in evolutionary rate between sites within HA. This suggests that residues close to the host cell receptor-binding region experience different evolutionary constraints compared to residues farther away from the receptor-binding region. It is possible that a similar  distance metric for enzymes might be effective for understanding the structural constraints of selection for active site. Residues close to the active site may experience constraints in the same way. Therefore although general biophysical properties have been demonstrated to pertain all proteins, there are additional structural constraints that effect site-wise variably within different types of proteins. Further research into the specific biophysical constraints of difference classes of proteins (ex. viral, enzymes) will help better our understanding of how protein biophysics affects the evolution of proteins.

@@

    \begin{figure}[H]
            \centerline{\includegraphics[width=7.5in]{entropy_cn_cor.pdf}}     
            \caption{Correlations between Contact Number (CN) and Entropy. For each protein we calculate the Spearman Correlation coefficient between CN and entropy at each site within the protein. A) Comparison between the correlation coefficients and mean entropy of site in each protein. The line indicates a linear regression through the enzyme proteins with mean entropy as a single predictor of the spearman correlations. B) Comparison between correlation coefficients and the variance of entropy of each protein. The enzyme proteins are colored in black and the virus proteins are visualized in red. For both WCN and CN the viral proteins have lower mean entropy and variance of entropy. The line indicates a linear regression through the enzyme proteins with variance entropy as a single predictor of the spearman correlations. Proteins with a larger variance in site entropy among sites tend to smaller CN-Entropy correlations in magnitude. Note: The entropy values in this manuscript are different than in \cite{Shahmoradietal2014}. Those entropy values were scales by a a factor of $1/\sum_j P_{ij}$. }
            \label{fig:entropy_cn_cor}
    \end{figure}

@@
